Deep Variation Transformation for Foreground Detection

### 2019-02-11 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.blg 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

% \begin{spacing}{2.0}
\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyzed the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, using a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL).
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
    In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input to a fully convolutional network \textcolor{blue}{space} (FCN) to find a transformation of pixels' variation.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a linear classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
Resulting from the global analysis of pixel variations and the strong learning ability of deep learning networks,
the proposed approach adaptively learns a good transformation from pixel variations to label and generate good performance in diverse natural scenes.
%    \textcolor{red}{
% Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
%    the proposed approach adaptively generates superior performances in diverse nature scenes.}
%
Comprehensive experiments on several standard benchmarks demonstrate the superiority of the proposed approach compared to state-of-the-art deep learning and traditional methods.
%
\end{abstract}

@@

\section{Experiments}
\label{sec5}
In this section, we describe comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}.
%
CDnet is the largest dataset for foreground detection as far as we are kown, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on. 
The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, containing 10 high resolution videos. 
For each video, one or two persons appear in the scene with clothes having color similar to the background.

@@

Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
To keep the length of this paper reasonable, only several typical videos are selected for the qualitative comparisons and discussion. 
In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in \reffig{results_chart}. 
Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
In contrast, benefiting from the strong learning ability of Deep Learning networks, DeepBS successfully detects the people. 
Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
In contrast, the proposed approach performs better from others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence. 
Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
Thus the proposed approach achieves promising performance for the canoe video.

@@

\section{Conclusion}
\label{sec6}
In this paper, we proposed a novel foreground detection approach based on our proposed variation transformation learning.
%
Transformation learning focused on learning a transformation from pixel variations to the probability of pixels belonging to foreground or background.
%
The global variation patterns of pixel observation is learned for better classification of pixels.
%
In particular, a FCN network and a novel variation transformation learning framework is proposed to efficiently combine the temporal coherence and distribution information of pixels over a long period of time. 
%
Comparisons with other traditional and deep learning methods shows that our DPVTL algorithms significantly improves performance on several challenging scenes.
%The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.

@@

% \end{spacing}

>>>>

% \begin{spacing}{2.0}
\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyzed the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, using a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL).
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
    In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input to a fully convolutional network space (FCN) to find a transformation of pixels' variation.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a linear classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
Resulting from the global analysis of pixel variations and the strong learning ability of deep learning networks,
the proposed approach adaptively learns a good transformation from pixel variations to label and generate good performance in diverse natural scenes.
%    \textcolor{red}{
% Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
%    the proposed approach adaptively generates superior performances in diverse nature scenes.}
%
Comprehensive experiments on several standard benchmarks demonstrate the superiority of the proposed approach compared to state-of-the-art deep learning and traditional methods.
%
\end{abstract}

@@

\section{Experiments}
\label{sec5}
In this section, we describe comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}.
%
CDnet is the largest dataset for foreground detection as far as we know, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on. 
The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, containing 10 high resolution videos. 
For each video, one or two persons appear in the scene with clothes having color similar to the background.

@@

Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
To keep the length of this paper reasonable, only several typical videos are selected for the qualitative comparisons and discussion. 
In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in \reffig{results_chart}. 
Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
In contrast, benefiting from the strong learning ability of Deep Learning networks, DeepBS successfully detects the people. 
Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
In contrast, the proposed approach performs better than others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence. 
Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
Thus the proposed approach achieves promising performance for the canoe video.

@@

\section{Conclusion}
\label{sec6}
In this paper, we proposed a novel foreground detection approach based on our proposed variation transformation learning.
%
Transformation learning focused on learning a transformation from pixel variations to the probability of pixels belonging to the foreground or background.
%
The global variation patterns of pixel observation is learned for better classification of pixels.
%
In particular, a FCN network and a novel variation transformation learning framework is proposed to efficiently combine the temporal coherence and distribution information of pixels over a long period of time. 
%
Comparisons with other traditional and deep learning methods shows that our DPVTL algorithm significantly improves performance on several challenging scenes.
%The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.

@@
